Report on Certificate Tools

### 2016-10-26 TEX/draft.tex
Added Makecert

\section{General}
%TABLE START
\begin{table}[h!]
\centering
\caption{Overwiew General}
\label{my-label}
\begin{adjustbox}{max width=\textwidth}
\begin{tabular}{|c|c|c|c|c|}
\hline
                        & \multicolumn{4}{c|}{General}                                                                               \\ \cline{2-5} 
\multirow{-2}{*}{Tools} & Type   & View + info                                        & License & Operating System                   \\ \hline
OpenSSL                 & PKCS12 & \cellcolor[HTML]{34FF34}Yes                        & Public  & \cellcolor[HTML]{34FF34}Both       \\ \hline
Keytool                 & JKS    & \cellcolor[HTML]{34FF34}{\color[HTML]{000000} Yes} & Public  & \cellcolor[HTML]{34FF34}Both       \\ \hline
GnuPG                   &        &                                                    &         &                                    \\ \hline
Keystore Explorer       & Both   & \cellcolor[HTML]{34FF34}Yes                        & Public  & \cellcolor[HTML]{FFC702}Win | OS X \\ \hline
XCA                     & PKCS12 & \cellcolor[HTML]{34FF34}Yes                        & Public  & \cellcolor[HTML]{34FF34}Both       \\ \hline
GnuTLS                  & PKCS12 & \cellcolor[HTML]{34FF34}Yes                        & Public  & \cellcolor[HTML]{FFC702}LINUX       \\ \hline
\end{tabular}
\end{adjustbox}
\end{table}
%TABLE END

@@

\subsection{Keys, certificates and basic constraints}
%TABLE START
\begin{table}[h!]
\centering
\caption{Generation of keys and certificates and basic constrints}
\begin{adjustbox}{max width=\textwidth}
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline
                       & \multicolumn{4}{c|}{Generate keys}                                                                                                                             & \multicolumn{2}{c|}{Basic Constraints}                    \\ \cline{2-7} 
\multirow{-2}{*}{Tool} & \begin{tabular}[c]{@{}c@{}}+\\  self-signed certificate\end{tabular} & + CSR                       & Specify length              & Specify algorithm           & Specify Type                & Specify path length         \\ \hline
OpenSSL                & \cellcolor[HTML]{34FF34}Yes                                          & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes \\ \hline
Keytool                & \cellcolor[HTML]{34FF34}Yes                                          & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes \\ \hline
GnuPG                  &                                                                      &                             &                             &                             &                             &                             \\ \hline
Keystore explorer      & \cellcolor[HTML]{34FF34}Yes                                          & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes \\ \hline
XCA                    & \cellcolor[HTML]{34FF34}Yes                                          & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes \\ \hline
GnuTLS                 & \cellcolor[HTML]{34FF34}Yes                                          & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes \\ \hline
\end{tabular}
\end{adjustbox}
\end{table}
%TABLE END

@@

%TABLE START
\begin{table}[h!]
\centering
\caption{Specifications}
\label{my-label}
\begin{adjustbox}{max width=\textwidth}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
                       &                               &                                          &                                                &                                            &                                                                             \\
\multirow{-2}{*}{Tool} & \multirow{-2}{*}{CSR signing} & \multirow{-2}{*}{Privkey + signed chain} & \multirow{-2}{*}{Specify certificate validity} & \multirow{-2}{*}{SAN for end certificates} & \multirow{-2}{*}{\begin{tabular}[c]{@{}c@{}}Support for\\ CSP\end{tabular}} \\ \hline
OpenSSL                & \cellcolor[HTML]{34FF34}Yes   & \cellcolor[HTML]{34FF34}Yes              & \cellcolor[HTML]{34FF34}Yes                    & \cellcolor[HTML]{34FF34}Yes                & \cellcolor[HTML]{34FF34}Yes                                                 \\ \hline
Keytool                & \cellcolor[HTML]{34FF34}Yes   & \cellcolor[HTML]{34FF34}Yes              & \cellcolor[HTML]{34FF34}Yes                    & \cellcolor[HTML]{34FF34}Yes                & \cellcolor[HTML]{34FF34}Yes                                                 \\ \hline
GnuPG                  &                               &                                          &                                                &                                            &                                                                             \\ \hline
Keystore explorer      & \cellcolor[HTML]{34FF34}Yes   & \cellcolor[HTML]{34FF34}Yes              & \cellcolor[HTML]{34FF34}Yes                    & \cellcolor[HTML]{34FF34}Yes                & \cellcolor[HTML]{FE0000}No                                                  \\ \hline
XCA                    & \cellcolor[HTML]{34FF34}Yes   & \cellcolor[HTML]{34FF34}Yes              & \cellcolor[HTML]{34FF34}Yes                    & \cellcolor[HTML]{34FF34}Yes                & ???                                                                         \\ \hline
GnuTLS                 & \cellcolor[HTML]{34FF34}Yes   & ???	                                  & \cellcolor[HTML]{34FF34}Yes                    & \cellcolor[HTML]{34FF34}Yes                & \cellcolor[HTML]{FE0000}No                                                  \\ \hline
\end{tabular}
\end{adjustbox}
\end{table}
%TABLE END

@@

%TABLE START
\begin{table}[h!]
\centering
\caption{Conversions}
\label{my-label}
\begin{adjustbox}{max width=\textwidth}
\begin{tabular}{|c|c|c|c|c|}
\hline
                        & \multicolumn{4}{c|}{Conversions}                                                                                                                                            \\ \cline{2-5} 
                        & \multicolumn{2}{c|}{Exporting}                                 &                                         &                                                                  \\ \cline{2-3}
\multirow{-3}{*}{Tools} & Certificate/chain only from file & Private key only            & \multirow{-2}{*}{Direct JKS and PKCS12} & \multirow{-2}{*}{Import certificate and private key into a file} \\ \hline
OpenSSL                 & \cellcolor[HTML]{34FF34}Yes      & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{FF3A3A}No              & \cellcolor[HTML]{34FF34}Yes                                      \\ \hline
Keygen                  & \cellcolor[HTML]{34FF34}Yes      & \cellcolor[HTML]{FE0000}No  & \cellcolor[HTML]{34FF34}Yes             & \cellcolor[HTML]{34FF34}Yes                                      \\ \hline
GnuPG                   &                                  &                             &                                         &                                                                  \\ \hline
Keystore explorer       & \cellcolor[HTML]{34FF34}Yes      & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes             & \cellcolor[HTML]{34FF34}Yes                                      \\ \hline
XCA                     & \cellcolor[HTML]{34FF34}Yes      & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{FF3A3A}No              & \cellcolor[HTML]{34FF34}Yes                                      \\ \hline
GnuTLS                  & \cellcolor[HTML]{34FF34}Yes      & \cellcolor[HTML]{FF3A3A}No  & \cellcolor[HTML]{FF3A3A}No              & \cellcolor[HTML]{34FF34}Yes                                      \\ \hline
\end{tabular}
\end{adjustbox}
\end{table}
%TABLE END

@@

>>>>

\section{General}
%TABLE START
\begin{table}[h!]
\centering
\caption{Overwiew General}
\label{my-label}
\begin{adjustbox}{max width=\textwidth}
\begin{tabular}{|c|c|c|c|c|}
\hline
                        & \multicolumn{4}{c|}{General}                                                                               \\ \cline{2-5} 
\multirow{-2}{*}{Tools} & Type   & View + info                                        & License & Operating System                   \\ \hline
OpenSSL                 & PKCS12 & \cellcolor[HTML]{34FF34}Yes                        & Public  & \cellcolor[HTML]{34FF34}Both       \\ \hline
Keytool                 & JKS    & \cellcolor[HTML]{34FF34}{\color[HTML]{000000} Yes} & Public  & \cellcolor[HTML]{34FF34}Both       \\ \hline
GnuPG                   &        &                                                    &         &                                    \\ \hline
Keystore Explorer       & Both   & \cellcolor[HTML]{34FF34}Yes                        & Public  & \cellcolor[HTML]{FFC702}Win | OS X \\ \hline
XCA                     & PKCS12 & \cellcolor[HTML]{34FF34}Yes                        & Public  & \cellcolor[HTML]{34FF34}Both       \\ \hline
GnuTLS                  & PKCS12 & \cellcolor[HTML]{34FF34}Yes                        & Public  & \cellcolor[HTML]{FFC702}LINUX      \\ \hline
Makecert                & PKCS12 & \cellcolor[HTML]{FE0000}No			      & Public  & \cellcolor[HTML]{FFC702}Windows    \\ \hline
\end{tabular}
\end{adjustbox}
\end{table}
%TABLE END

@@

\subsection{Keys, certificates and basic constraints}
%TABLE START
\begin{table}[h!]
\centering
\caption{Generation of keys and certificates and basic constrints}
\begin{adjustbox}{max width=\textwidth}
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline
                       & \multicolumn{4}{c|}{Generate keys}                                                                                                                             & \multicolumn{2}{c|}{Basic Constraints}                    \\ \cline{2-7} 
\multirow{-2}{*}{Tool} & \begin{tabular}[c]{@{}c@{}}+\\  self-signed certificate\end{tabular} & + CSR                       & Specify length              & Specify algorithm           & Specify Type                & Specify path length         \\ \hline
OpenSSL                & \cellcolor[HTML]{34FF34}Yes                                          & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes \\ \hline
Keytool                & \cellcolor[HTML]{34FF34}Yes                                          & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes \\ \hline
GnuPG                  &                                                                      &                             &                             &                             &                             &                             \\ \hline
Keystore explorer      & \cellcolor[HTML]{34FF34}Yes                                          & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes \\ \hline
XCA                    & \cellcolor[HTML]{34FF34}Yes                                          & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes \\ \hline
GnuTLS                 & \cellcolor[HTML]{34FF34}Yes                                          & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes \\ \hline
Makecert               & \cellcolor[HTML]{34FF34}Yes					      & \cellcolor[HTML]{FE0000}No  & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{FFFFFF}    & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes \\ \hline
\end{tabular}
\end{adjustbox}
\end{table}
%TABLE END

@@

%TABLE START
\begin{table}[h!]
\centering
\caption{Specifications}
\label{my-label}
\begin{adjustbox}{max width=\textwidth}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
                       &                               &                                          &                                                &                                            &                                                                             \\
\multirow{-2}{*}{Tool} & \multirow{-2}{*}{CSR signing} & \multirow{-2}{*}{Privkey + signed chain} & \multirow{-2}{*}{Specify certificate validity} & \multirow{-2}{*}{SAN for end certificates} & \multirow{-2}{*}{\begin{tabular}[c]{@{}c@{}}Support for\\ CSP\end{tabular}} \\ \hline
OpenSSL                & \cellcolor[HTML]{34FF34}Yes   & \cellcolor[HTML]{34FF34}Yes              & \cellcolor[HTML]{34FF34}Yes                    & \cellcolor[HTML]{34FF34}Yes                & \cellcolor[HTML]{34FF34}Yes                                                 \\ \hline
Keytool                & \cellcolor[HTML]{34FF34}Yes   & \cellcolor[HTML]{34FF34}Yes              & \cellcolor[HTML]{34FF34}Yes                    & \cellcolor[HTML]{34FF34}Yes                & \cellcolor[HTML]{34FF34}Yes                                                 \\ \hline
GnuPG                  &                               &                                          &                                                &                                            &                                                                             \\ \hline
Keystore explorer      & \cellcolor[HTML]{34FF34}Yes   & \cellcolor[HTML]{34FF34}Yes              & \cellcolor[HTML]{34FF34}Yes                    & \cellcolor[HTML]{34FF34}Yes                & \cellcolor[HTML]{FE0000}No                                                  \\ \hline
XCA                    & \cellcolor[HTML]{34FF34}Yes   & \cellcolor[HTML]{34FF34}Yes              & \cellcolor[HTML]{34FF34}Yes                    & \cellcolor[HTML]{34FF34}Yes                & ???                                                                         \\ \hline
GnuTLS                 & \cellcolor[HTML]{34FF34}Yes   & ???	                                  & \cellcolor[HTML]{34FF34}Yes                    & \cellcolor[HTML]{34FF34}Yes                & \cellcolor[HTML]{FE0000}No                                                  \\ \hline
Makecert	       & \cellcolor[HTML]{FE0000}No    &   \cellcolor[HTML]{FE0000}No	 	  & \cellcolor[HTML]{34FF34}Yes			   & \cellcolor[HTML]{FE0000}No			& \cellcolor[HTML]{34FF34}Yes						      \\ \hline
\end{tabular}
\end{adjustbox}
\end{table}
%TABLE END

@@

%TABLE START
\begin{table}[h!]
\centering
\caption{Conversions}
\label{my-label}
\begin{adjustbox}{max width=\textwidth}
\begin{tabular}{|c|c|c|c|c|}
\hline
                        & \multicolumn{4}{c|}{Conversions}                                                                                                                                            \\ \cline{2-5} 
                        & \multicolumn{2}{c|}{Exporting}                                 &                                         &                                                                  \\ \cline{2-3}
\multirow{-3}{*}{Tools} & Certificate/chain only from file & Private key only            & \multirow{-2}{*}{Direct JKS and PKCS12} & \multirow{-2}{*}{Import certificate and private key into a file} \\ \hline
OpenSSL                 & \cellcolor[HTML]{34FF34}Yes      & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{FF3A3A}No              & \cellcolor[HTML]{34FF34}Yes                                      \\ \hline
Keygen                  & \cellcolor[HTML]{34FF34}Yes      & \cellcolor[HTML]{FE0000}No  & \cellcolor[HTML]{34FF34}Yes             & \cellcolor[HTML]{34FF34}Yes                                      \\ \hline
GnuPG                   &                                  &                             &                                         &                                                                  \\ \hline
Keystore explorer       & \cellcolor[HTML]{34FF34}Yes      & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes             & \cellcolor[HTML]{34FF34}Yes                                      \\ \hline
XCA                     & \cellcolor[HTML]{34FF34}Yes      & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{FF3A3A}No              & \cellcolor[HTML]{34FF34}Yes                                      \\ \hline
GnuTLS                  & \cellcolor[HTML]{34FF34}Yes      & \cellcolor[HTML]{FF3A3A}No  & \cellcolor[HTML]{FF3A3A}No              & \cellcolor[HTML]{34FF34}Yes                                      \\ \hline
Makecert		& \cellcolor[HTML]{FE0000}No	   & \cellcolor[HTML]{FE0000}No  & \cellcolor[HTML]{FE0000}No		   & \cellcolor[HTML]{34FF34}Yes				      \\ \hline
\end{tabular}
\end{adjustbox}
\end{table}
%TABLE END

@@

\chapter{Makecert}

  \subsection{Type}
Makecert can work with PKCS\#12 type files, however  default output is in \verb+.cer+ for certificate and \verb+.pvk+ for private key. To tie together key and certificate you need to combine them into PKCS\#12 type file with \verb+pvk2pfx+ tool (which is also part of Windows SDK). In addition to use the tool you need to start a Developer Command Prompt for Visual Studio (on Windows 10). 
\\ 
In addition to that makecert is deprecated itself as cited on MSDN MakeCert site.
  \subsection{View and information}
Makecert does not allow user to view created certificates or any information about them whatsoever.
  \subsection{License}
It is free to use, falls under the Windows SDK.

      \paragraph{Self-signed certificate}
Generating key and self-signed certificate that can be used as CA is not straightforward with Makecert.
\begin{verbatim}
makecert -n "CN=Common Name, OU=Organization Unit, O=..." -cy [authority|end] \
	 -a [sha256|sha384|sha512] -sv <key_file_name>.pvk -r \
	 -len <int key_length> <cert_name>.cer
\end{verbatim}

Where -n sets credentials, -cy defines certificate type, -a chooses signature algorithm, -sv chooses name for file where the private key is stored, -r to create a self-signed certificate, -len for key length and without option choose the filename.

After entering this command you will be prompted to enter private key file password.

After creating certificate and private key file successfully to use self-signed certificate as a CA you need to join certificate file and private key into PKCS\#12 type file. This is made by using a pvk2pfx tool already implemented in Windows SDK.
\begin{verbatim}
pvk2pfx -spc <cert_file> -pvk <key_file>.pvk -pfx <pfx_file_name>.pfx \
        [-pi <key_password> -po <pfx_password]
\end{verbatim}

-pi option is used if there is a password on key file, -po is desired pfx file password. If no password for pfx is given makecert defaults it to key file password.

      \paragraph{Certificate Signing Request}
It is not possible to create a CSR using Makecert.
      \paragraph{Specify length}
Length is specified by \verb+-len <int key_length>+ option.
      \paragraph{Specify algorithm}
To specify hash algorithm use \verb+-a [sha256|sha384|sha512]+ option. Supported are also SHA1 and MD5 but those are considered unsafe.

To specify key algorithm you must change CSP.
    \subsubsection{Basic constraints}

      \paragraph{Specify Type}
It is possible with \verb+-cy [authority|end]+ option.
      \paragraph{Specify path length}
Path length is specified by \verb+-h <int length>+ option while creating a certificate.
  \subsection{Specifications}

    \subsubsection{Certificate Signing Request signing}
Not possible.
    \subsubsection{Create combination of private key and signed chain}
Not possible.
    \subsubsection{Specify certificate validity}
Defaults from date of creation until 2039, to change use \verb+-b <mm/dd/yyyy -> from> -e <mm/dd/yyyy -> until>+ option.
Alternatively you can use \verb+-m <int months>+ option where you choose for how many months the certificate will be valid.
    \subsubsection{Setting Subject Alternative Name for end certificates}
Not possible.
    \subsubsection{Support for Cryptographic Service Provider}
There is support for CSP in makecert by using \verb+-sp <provider_name> -sy <provider_type>+ defines the CryptoAPI provider for subject.
\section{Conversions}

    \subsubsection{Certificate or certificate chain from a file}
Not possible.
    \subsubsection{Private key only}
Private key is stored and generated while generating a certificate but the type .pvk is uncommon.
  \subsection{Direct conversion between Java Keystore and PKCS\#12 file}
Not possible.
  \subsection{Importing certificates and keys into storage files}
For importing of keys and certificates into PKCS\#12 file, use pvk2pfx as in generating self-signed part. There is just option to add 1 certificate and 1 private key into a file.
